\paragraph{Definitions}
\begin{itemize}
	\item User: Someone registered to the system
	\item Visitor: user that is not registered nor logged in
	\item System: the union of software and hardware to be developed and implemented
	\item Parking area: it is a reserved area, predefine by the system, where I can park the car but I cannot recharge it.
	\item Safe area: it is a reserved area, predefine by the system, where I can park the car and plug it into charge.
	\item Free car: The car is visible on the map and available for a reservation
	\item Reserved car: The car is not visible on the map and the user who reserved it didn't access yet.
	\item Internet: The Internet is the global system of interconnected computer networks that use the Internet protocol suite (TCP/IP) to link billions of devices worldwide.
	\item Service: The functionalities offered by myTaxiService via software appli- cations to passengers and taxi drivers.
	\item System: The whole hardware and software parts that together deliver myTaxiService as a service to passengers and taxi drivers.
	\item Smartphone: A mobile phone with an advanced mobile operating sys- tems, which combines features of a personal computer operating system with other features useful for mobile or handheld use.
	\item Application: A computer program (i.e. a piece of software) that per- forms a group of coordinated functions, tasks, or activities for the benefit of the user.
	\item World Wide Web: Also referred as web, is an information space where documents and other web resources are identified by URLs, interlinked by hypertext links, and can be accessed via the Internet.
	\item Web Page: A web document that is suitable for the World Wide Web and the web browser.
	\item Web Server: An information technology that processes requests via HTTP and stores, processes and deliver web pages to clients.

\end{itemize}
\paragraph{Acronyms}
\begin{itemize}
	\item RASD: requirements analysis and specification document
	\item AES: Advanced Encryption Standard
	\item FIFO: First In First Out
	\item ETA: estimated time of arrival
	\item API: application programming interface
	\item GPS: Global Positioning System
	 IEEE: Institute of Electrical and Electronics Engineers.
	\item SRS: Software Requirements Specification, document based on IEEE 830.
	\item RASD: Requirements Analysis and Specification Document, also known as SRS.
	\item UML: Unified Modeling Language.
	\item Wi-Fi: Wireless Fidelity, technology for local area wireless computer networking technology based on IEEE 802.11 standard.
	\item WiMAX: Worldwide Interoperability for Microwave Access, technology based on IEEE 802.16 standard.
	\item API: Application Programming Interface, a set of public accessible func- tions, protocols and tools provided by a specific application for building software applications.
	\item GPS: Global Positioning System.
	\item DBMS: Database Management System.

\end{itemize}
