The software described in this document is a new digital management system for car-sharing service that exclusively use electrical cars. It has as main goal the simplification of the car sharing service and the management of the reservation and the usage of the car. It can be applied to different small and big city and even in a large urban area and it's composed by a mobile application who permit to the user to interact with the system and a web platform that explain to the users all the procedure to access to the service. 
There are three type of users:
\begin{itemize}
	\item Visitors: all the visitors have acces to the login and registration page on the mobile application and will be also able to visit the information part of the website that include FAQ page and Home page
	\item Registered user: this set can be split in two different subcategory:
		\begin{itemize}
			\item Driver: this user can rent a car, invite other user to participate in the ride and finally can report problems.
			\item Passenger: this type of user is invited by the driver and can, after a login, participate to a ride. 
		\end{itemize}
\end{itemize}
The main difference between a driver and a passenger is that the first one had enter its driver license and it can drive covered by the insurance. The second one can just participate to a ride by scanning a QRCode showed in the inboard computer of the car.
Besides the specific user interfaces for passengers and taxi drivers, the system offers also APIs to enable the development of additional services on top of the basic one.